Efficient Calculation of Polynomial and Interaction Features on Sparse Matrices

### 2015-09-24 paper/paper2.tex
made more clear
table caption
.

\begin{sidewaysfigure*}[ht!]
    \centering
    \includegraphics[scale=0.5]{classifier_boundaries.png}
    \caption{Decision boundaries for four classifier types on four different datasets. The darker the color, the more certain the decision.
             The plain dataset is shown in the first column. Each other column is a type of classifier applied to that dataset. The classifier
             types are logistic regression, logistic regression with second degree polynomial features, RBF SVM, and gradient boosting with decision trees.
             The accuracy of each model is shown in the bottom right corner of that model's subplot.}
    \label{fig:boundaries}
\end{sidewaysfigure*}

@@

It's often the case in a machine learning setting that the input matrix has near uniform density across its rows.
For example, if the matrix is sparse due to one-of-m encoding (also known as one-hot vectors), each row vector will
have the same number of nonzero components.

@@

\begin{figure*}[ht!]
    \includegraphics[scale=0.3]{benchmark_results.png}
    \caption{This plot shows how long the sparse polynomial method took to run on matrices with 1000 rows of various dimensionalities and densities and compared to the scikit-learn PolynomialFeatures class on various dimensionalities.}
    \label{fig:benchmark}
    \centering
\end{figure*}

@@

\begin{center}
    \begin{tabular}{c | c | c} \label{table:results}
 %       \hline
        dataset             & 20newsgroups  & connect-4 \\ \hline
        instances           & 11314        & 67557    \\ \hline
        features            & 130107       & 126       \\ \hline
        polynomial features & 8463980778 & 8,127     \\ \hline
        density             & 0.12          & 0.11      \\ \hline
        dense space (MB)    & Memory Error  & 4191      \\ \hline
        sparse space (MB)   & 5333          & 735       \\ \hline
        dense time (s)      & Memory Error  & 26        \\ \hline
        sparse time (s)     & 109           & 44        \\ \hline
%        \hline
    \end{tabular}
\end{center}

>>>>

\begin{sidewaysfigure*}[ht!, numbered]
    \centering
    \includegraphics[scale=0.5]{classifier_boundaries.png}
    \caption{Decision boundaries for four classifier types on four different datasets. The darker the color, the more certain the decision.
             The plain dataset is shown in the first column. Each other column is a type of classifier applied to that dataset. The classifier
             types are logistic regression, logistic regression with second degree polynomial features, RBF SVM, and gradient boosting with decision trees.
             The accuracy of each model is shown in the bottom right corner of that model's subplot.}
    \label{fig:boundaries}
\end{sidewaysfigure*}

@@

In machine learning, an input matrix often has near uniform density across its rows.
For example, if the matrix is sparse due to one-of-m encoding (also known as one-hot vectors), each row vector will
have the same number of nonzero components.

@@

\begin{figure*}[ht!, numbered]
    \includegraphics[scale=0.3]{benchmark_results.png}
    \caption{This plot shows how long the sparse polynomial method took to run on matrices with 1000 rows of various dimensionalities and densities and compared to the scikit-learn PolynomialFeatures class on various dimensionalities.}
    \label{fig:benchmark}
    \centering
\end{figure*}

@@

\begin{table}
    \centering
    \begin{tabular}[numbered]{c | c | c} \label{table:results}
 %       \hline
        dataset             & 20newsgroups  & connect-4 \\ \hline
        instances           & 11314        & 67557    \\ \hline
        features            & 130107       & 126       \\ \hline
        polynomial features & 8463980778 & 8,127     \\ \hline
        density             & 0.12          & 0.11      \\ \hline
        dense space (MB)    & Memory Error  & 4191      \\ \hline
        sparse space (MB)   & 5333          & 735       \\ \hline
        dense time (s)      & Memory Error  & 26        \\ \hline
        sparse time (s)     & 109           & 44        \\ \hline
%        \hline
    \end{tabular}
    \caption{Time and space comparison of second degree polynomial feature calculation between the sparse method and scikit-learn.}
\end{table}
